\input{../default_settings.tex}
\usepackage[left=48pt,right=46pt]{geometry}

\title{\lstinline!testgen/runs-2014-07-27__04_03_21! \\\vspace{2pt}\small{\rm \today}}
\begin{document}
\maketitle

results from \lstinline!testgen/runs-2014-07-27__04_03_21!

\section{Validate Solution}

\begin{itemize}
	\item size attributes on relations (1406448497.essence), sets (1406448497.essence).
	
	\item inner most set not converted to matrix in solution translation.
	\begin{lst:essence}[breaklines=true,caption=1406468690.essence]
    Expected: matrix indexed by [int, int] of relation (set of int)
    Found:    matrix indexed by [int, int] of relation (matrix indexed by [int] of int)
	\end{lst:essence}
	

	
\end{itemize}

\section{Inconsistent}
\begin{itemize}
	\item Only 1 of out of the 3 eprimes are satisfiable, when they should all be. 
	\begin{lst:essence}[breaklines=true,caption=1406438642.essence]
	language Essence 1.3
	find var0:
	        relation of
	            (relation (size 1) of (int(3..5) * int(4..4)) *
	             matrix indexed by [int(3..5)] of int(5..5) * function int(2..5) --> int(5..5))
	\end{lst:essence}

	\item 5 eprimes, 4 are satisfiable, one is not, when they should all be satisfiable
	\begin{lst:essence}[breaklines=true,caption=1406470083.essence]
	language Essence 1.3

	find var0:
	        function (surjective, minSize 4)
	            set of int(2..3) --> matrix indexed by [int(5..5)] of int(5..5)
	\end{lst:essence}

	\item  2 eprimes, only 1 satisfiable when they both should be satisfiable.
	\begin{lst:essence}[breaklines=true,caption=1406470239.essence]
	language Essence 1.3
	find var0: set (size 3) of function int(2..3) --> int(4..4)
	\end{lst:essence}
	
	
\end{itemize}

\section{Solution Translation}

\begin{itemize}
	\item \texttt{partition from matrix, partition from set} (1406434592.essence)
	\item \texttt{function set --> function -> int } (1406435421.essence)
	\item \texttt{relation of  function -> function -> relation } (1406449575.essence)
\end{itemize} 


\section{Misc}

\begin{itemize}
	\item If one of the eprimes timed out, it should not be used in the inconstant calculations (1406448933.essence).
	\item Always allow solution translation and solution validation?  solution translation is basically instant. solution validation can take a while if there are lots of constraints.  Same reason as above. 
\end{itemize}

\section{Missing Representation Rule}

\begin{lstlisting}[breaklines=True]
	1406324659
    No representation rule matches domain: find var2:
                                                   function (maxSize 3, minSize 2) int(2..2) --> int(1..3)

    1406333150
    No representation rule matches domain: find var0: partition (minNumParts 1) from int(4..4)

    1406333151
    No representation rule matches domain: find var0:
                                                   partition (maxPartSize 4) from int(4..4)

    1406333170
    No representation rule matches domain: find var1:
                                                   partition (partSize 1) from function (total) int(3..3) --> int(4..5)

    1406333198												   
    No representation rule matches domain: find var0:
                                                   function (injective, maxSize 2, surjective, total, minSize 3)
                                                       set (minSize 4) of int(3..5) --> set (maxSize 5) of int(5..5)

    1406333220
    No representation rule matches domain: function (total, minSize 1, injective,
                                                     size 3)
                                               int(3..4) --> int(2..4)

    No representation rule matches domain: find var1:
       partition (regular) from
           relation (minSize 4) of
               (matrix indexed by [int(3..5)] of partition (minNumParts 4,
                                                            partSize 1,
                                                            minPartSize 5) from
                                                     int(5..5))              
    1406332163
    No representation rule matches domain: find var2:
                                                   function (maxSize 3, minSize 2) int(2..2) --> int(1..3)

\end{lstlisting}



\bibliography{../extra}
\bibliographystyle{../splncs03}
\end{document}
