\input{../default_settings.tex}
\usepackage[left=48pt,right=46pt]{geometry}

\title{ \lstinline!testgen/runs-2014-07-26__02_24_31! \\\vspace{2pt}\small{\rm \today} \vspace{-0.5cm}}
\begin{document}
\maketitle

results from \lstinline!testgen/runs-2014-07-26__02_24_31!

\section{Improvements}

\begin{itemize}
	\item Removed duplicates models after generating $n$ random models, which saves repeated work.
	\item Solution validation. Check the solution are consistent with their domains e.g. sets can't have duplicates. Also verify the domain attributes are satisfied.  Solution validation founds some new bugs.
\end{itemize}

\section{Validate Solution}

\subsection{set attributes}

Using a combination of \texttt{maxSize, minSize and size} causes all 3 \texttt{eprime}s to have a solution when it should not. This was not caught be inconsistent from before since the bug affected all \texttt{epirime}s.


\begin{lst:essence}[caption=1406342762.essence]
summary/gErrorsSolve/validateSolution/1406342762_0001/1406342762.essence

language Essence 1.3

find var1: matrix indexed by [int(4..4), int(3..3)] of int(5..5)
find var0:
        set (size 1, minSize 4, maxSize 2) of
            function (total, surjective, minSize 1) int(1..1) --> int(5..5)
\end{lst:essence}

\begin{lstlisting}[breaklines=true,caption=Validating the solution]
Error for
Value:   {function(1 --> 5)}
Domain:  set (size 1, minSize 4, maxSize 2) of
             function (total, surjective, minSize 1) int(1..1) --> int(5..5)
Details:
  (minSize 4) not satisfied; Too few elements in set
      set (maxSize 2, minSize 4, size 1) of
          function (surjective, total, minSize 1) int(1..1) --> int(5..5)
      {function(1 --> 5)}
\end{lstlisting}


\ \\ The same problem occurs with relations 
\begin{lst:essence}[caption=1406343903.essence]
language Essence 1.3

find var1:
        set (size 4, minSize 1, maxSize 3) of
            relation (size 1, maxSize 3, minSize 2) of (int(4..4) * int(2..5))
find var0: set of matrix indexed by [int(3..5)] of int(2..4)

\end{lst:essence}

\subsection{Functions}

\begin{lst:essence}
language Essence 1.3

find var1: matrix indexed by [int(3..4)] of function int(5..5) --> int(2..3)
find var0: matrix indexed by [int(3..4)] of relation of (int(5..5) * int(2..2))
\end{lst:essence}

finds a bug in solution translation of \texttt{var1} when using \texttt{Function1DPartial}  giving the answer \texttt{[function(); int(3..4)]} instead of \texttt{[function(), function(); int(3..4)]}\\

\section{Inconsistent}

\subsection{ set of function (minSize 3)}

\begin{lst:essence}[caption=1406371130.essence]
language Essence 1.3
find var0: set of function (minSize 3) int(1..2) --> int(5..5)
\end{lst:essence}

3 eprimes,  2 are satisfiable and have solutions, 1 does not 

\ \\\subsection{relations and functions}

\begin{lst:essence}[caption=1406371836.essence]
language Essence 1.3

find var1:
        relation of (set of int(2..5) * matrix indexed by [int(2..5)] of int(4..4))
find var0: set of function int(2..5) --> int(3..3)

\end{lst:essence}

5 eprimes, 4 are satisfiable and have solutions, 1 does not.

\section{Solution Translation}

\begin{itemize}
	\item \texttt{ matrix indexed by [int(1..1)] of partition (size 2) from int(1..3)} ( 1406342749.essence, 1406375182.essence, 1406377200.essence, 1406378178.essence same)
	\item \texttt{relation of (function int(3..5) --> int(2..4))}  (comp, 1406345766.essence)
	\item very nested (1406372004.essence)
	\item 
\end{itemize}

\ \\\section{Misc}

\begin{itemize}
	\item Since we probably don't want errors which are too similar, one idea is to bias the away from area which have know errors.
	\item Biasing the selection of attributes to favour using less attributes. e.g $1/2$ for no attributes $1/4$ for 1 attributes $1/8$ for 2 attributes and so on. This give better test cases while still getting coverage.
	\item Random number don't look that random in some cases e.g \texttt{1406343927.essence} for example, check the rnd is being updated. Ironically still gave a good test case.
	\item Always allow solution translation and solution validation?  solution translation is basically instant. solution validation can take a while if there are lots of constraints.  
\end{itemize}

\bibliography{../extra}
\bibliographystyle{../splncs03}
\end{document}
